---
title: "MRSL D1 Knights 2025"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    vertical_layout: fill
    css: special_style.css
runtime: shiny
---

<!--------------------------------------------------------------------------------------
                                  SET UP: PACKAGES, FUCNTIONS, DATA LAOD 
------------------------------------------------------------------------------------> 

```{css, echo=FALSE}
.fluid-row {
  font-size: 5.9vw;
}
```

```{r}
knitr::opts_chunk$set(
  echo = F, warning = F, message = F
)
```

```{r}

PITCH_FILL = "#189505"

```

```{r packages }

library(readxl)
library(ggimage)
library(ggrepel)
library(ggsoccer)
library(shinyBS)
library(gridExtra)
library(ggthemes, quietly = TRUE)
library(htmltools, quietly = TRUE)
require(tidyverse)
library(plotly)
library(flexdashboard)
library(ggsoccer)
library(googleAuthR)
library(googlesheets4)
library(kableExtra)
library(shinydashboard)
library(scales)
library(fontawesome)
library(DT)
library(data.table)
library(rsconnect)
library(curl)

```

```{r help get access to the sheet, eval = F}
googlesheets4::gs4_deauth()

googlesheets4::gs4_auth()

```

```{r}
int_breaks <- function(x, n = 5) {
  l <- pretty(x, n)
  l[abs(l %% 1) < .Machine$double.eps ^ 0.5] 
}
```

```{r laod goals and assists data}

scores <- read_xlsx('Knights 2025 Scoring .xlsx', sheet = "Goals For")

scores$Group <- 
  with(scores, 
       case_when(
         `Player Position` %in% c("LW", "RW", "ST") ~ "Attackers", 
         `Player Position` %in% c("CM") ~ "Midfielders", 
         T ~ "Defenders"
       ))

scores$Group <- factor(scores$Group, levels = c("Defenders", "Midfielders", "Attackers"))

```

```{R load schedule and resutls data}
schedule <- 
  read_xlsx('Knights 2025 Scoring .xlsx', sheet = "Schedule")

schedule <- 
  schedule %>% 
  filter(Division == "D1" & !is.na(`Final Score` )) %>% 
  mutate(
    game = seq(from = 1, to = nrow(.), by = 1)
  )

schedule$`Home Score` = with(schedule, substr(`Final Score`, 2, 2))
schedule$`Home Score` <- as.numeric(schedule$`Home Score`)

schedule$`Away Score` = with(schedule, substr(`Final Score`, 4, 4))
schedule$`Away Score` <- as.numeric(schedule$`Away Score`)

schedule$our_goals = 
  with(schedule, 
       case_when(
         Home == "Knights" ~ `Home Score`, 
         T ~ `Away Score`
       ))
schedule$our_conceded = 
  with(schedule, 
       case_when(
         Home == "Knights" ~ `Away Score`, 
         T ~ `Home Score`
       ))

schedule$opponent = 
  with(schedule, 
       case_when(
         Home == "Knights" ~ Away, 
         T ~ Home
       ))

```

```{r}

nrow(schedule) -> games_played_N

games_played <- read_xlsx('2025 Knights Attendance and Game Locations.xlsx', sheet = "Attendance") 
games_played <- games_played[4:26,4:(4+games_played_N)]

colnames(games_played)[1] = "Player"

games_played %>% pivot_longer(cols = setdiff(colnames(.), "Player")) %>% 
  mutate(counter = ifelse(is.na(value), 1,0)) %>% 

  group_by(Player) %>% 
  summarise(
   games_played = sum(counter)
    ) %>% 
  ungroup() -> games_played

```

<!--------------------------------------------------------------------------------------
                                            DASHBOARD BODY
------------------------------------------------------------------------------------> 

Team Performance 
===

Column {data-width=200}
---

<!-- 
VALUE BOXES 
--> 

### Box

```{R}

Goals <- scores %>% filter(Action == "Goal") %>% nrow()
Goals_total = Goals

Games <- schedule %>% filter(Division == "D1") %>% nrow()

val <- 
  round(Goals / Games , 2)

cap <- paste0("Scored Goals Per Game <br/>", Goals, " goals in ", Games, " games")

flexdashboard::valueBox(value = val, caption = cap, color = "green", icon = "fa-bullseye")
```

### Box

```{r, warning=FALSE, message=FALSE}

val <- scores %>% filter(Action == "Goal") %>% filter(Player != "Own Goal") %>% select(Player) %>% unique() %>% nrow()

cap <- paste0("Players with 1+ Goals")

flexdashboard::valueBox(value = val, caption = cap, color = "blue", icon = 'fa-thumbs-up')
```

### Box

```{r, warning=FALSE, message=FALSE}

Goals <- schedule %>% filter(Division == "D1") %>% summarize(sum(our_conceded)) %>% unlist()
Games <- schedule %>% filter(Division == "D1") %>% nrow()

val <- 
  round(Goals / Games , 2)

cap <- paste0("Allowed Goals Per Game <br/>", Goals, " goals in ", Games, " games")

flexdashboard::valueBox(value = val, caption = cap, color = "red", icon = 'fa-hand-paper')
```

<!-- 
### Box

```{R}

cap <- paste0("Goals Due to Galacticos Forfeit")

flexdashboard::valueBox(value = 3, caption = cap, color = "orange", icon = 'fa-gear')
```

--> 

Column { .tabset data-width=450}
---

### Goals

```{r, warning=FALSE, message=FALSE}

scores %>% 
  filter(Action == "Goal") %>% 
  group_by(`Group`,
           .drop = FALSE) %>% 
  summarize(n = n(), 
            p = n()/nrow(.)) -> 
  
  goals

goals <- goals %>% arrange(`Group`)

goals$y_lab = c(25,50,75)
goals$x_lab = c(15,50,85)

goals$label = with(goals, paste0(n, " (", round(p, 4)*100, "%)"
                                     )
                     )


ggplot(data = goals, 
       aes(x = x_lab, y = y_lab, label = label)) +
  annotate_pitch(colour = "#999e9b") +
  theme_pitch(aspect_ratio = NULL) + 
  geom_point(color = "white") + 
  geom_text(size=12) + 
  theme(title = element_text(size = 20)) + 
  
  geom_segment(
    x = 67, xend = 67, 
    y = 10, yend = 90,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    colour = "red" # Also accepts "red", "blue' etc
  )+ 
  
  geom_segment(
    x = 31, xend = 31, 
    y = 10, yend = 90,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    colour = "red" # Also accepts "red", "blue' etc
  ) + 
  
  geom_segment(
    x = 15, xend = 25, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  ) + 
  
  geom_segment(
    x = 45, xend = 55, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  )+ 
  
  geom_segment(
    x = 75, xend = 85, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  ) + 
  
  theme(text = element_text(size = 20)) + 
  ggtitle(
    "Positional Origin of Goals: Defenders | Midfielders | Attackers"
  ) -> g1 
```



```{r, warning=FALSE, message=FALSE}

scores %>% 
  filter(Action == "Goal") %>% 
  group_by(`Position`, `Group`) %>% 
  summarize(n = n(), 
            p = n()/nrow(.)) %>% 
  ungroup() %>% 
  arrange(n) %>% 
  mutate(id = seq(from = 1, to = nrow(.), by = 1), 
         row_descr = 
           paste0(
             Group, " from \n ", Position
           ), 
         row_descr2 = 
           factor(
             paste0(
               Group, " from \n ", Position
             ), 
             levels = 
               paste0(
                 Group, " from \n ", Position
               )
           )
         ) -> goals


ggplot(data = goals, aes(x = row_descr2, y = n)) + 
  geom_col(
    color = "grey", fill = "blue"
  ) + 
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 20)) + 
  
  scale_y_continuous(
    breaks = seq(from = min(goals$n), to = max(goals$n), by = 2)
  ) + 
  ylab("Number of Goals") +
  
  xlab("") + 
  
  ggtitle("Distribution of Goals by Location and Position") -> g2

```



```{r,fig.width=10, fig.height=12}


grid.arrange(g1, g2, nrow = 2)

```

### Assists

```{r, warning=FALSE, message=FALSE}
scores %>% 
  filter(Action == "Assist") %>% 
  group_by(`Group`,
           .drop = FALSE) %>% 
  summarize(n = n(), 
            p = n()/nrow(.)) -> 
  
  assists2

assists2 <- assists2 %>% arrange(`Group`)

assists2$y_lab = c(25,50,75)
assists2$x_lab = c(15,50,85)

assists2$label = with(assists2, paste0(n, " (", round(p, 4)*100, "%)"
                                     )
                     )


ggplot(data = assists2, 
       aes(x = x_lab, y = y_lab, label = label)) +
  annotate_pitch(colour = "#999e9b") +
  theme_pitch(aspect_ratio = NULL) + 
  geom_point(color = "white") + 
  geom_text(size=12) + 
  theme(title = element_text(size = 20)) + 
  
  geom_segment(
    x = 67, xend = 67, 
    y = 10, yend = 90,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    colour = "red" # Also accepts "red", "blue' etc
  )+ 
  
  geom_segment(
    x = 31, xend = 31, 
    y = 10, yend = 90,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    colour = "red" # Also accepts "red", "blue' etc
  ) + 
  
  geom_segment(
    x = 15, xend = 25, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  ) + 
  
  geom_segment(
    x = 45, xend = 55, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  )+ 
  
  geom_segment(
    x = 75, xend = 85, 
    y = 85, yend = 85,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = 1, 
    arrow = arrow(length = unit(0.1, "inches")),
    colour = PITCH_FILL # Also accepts "red", "blue' etc
  ) + 
  ggtitle(
    "Positional Origin of Assists: \n  Defenders | Midfielders | Attackers"
  ) -> a1
```

```{r, warning=FALSE, message=FALSE}
scores %>% 
  filter(Action == "Assist") %>% 
  group_by(`Field Part`, .drop = FALSE) %>% 
  summarize(n = n(), 
            p = n()/nrow(.)) -> 
  
  assists

assists <- assists %>% arrange(`Field Part`)

assists$y_lab = c(85,50,15)
assists$x_lab = c(75,75,75)

assists$label = with(assists, paste0(n, " (", round(p, 4)*100, "%)"
                                     )
                     )


ggplot(data = assists, 
       aes(x = x_lab, y = y_lab, label = label)) +
  annotate_pitch(colour = "#999e9b") +
  theme_pitch(aspect_ratio = NULL) + 
  geom_point(color = "white") + 
  geom_text(size=12) + 
  theme(title = element_text(size = 20)) + 
  
  geom_segment(
    x = 30, xend = 89, 
    y = 67, yend = 67,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    arrow = arrow(length = unit(0.3, "inches")),
    colour = "blue" # Also accepts "red", "blue' etc
  )+ 
  
  geom_segment(
    x = 30, xend = 89, 
    y = 33, yend = 33,
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    linetype = "dashed", 
    size = 2, 
    arrow = arrow(length = unit(0.3, "inches")),
    colour = "blue" # Also accepts "red", "blue' etc
  ) + 
  ggtitle(
    "Directional Origin of Assists: \n Left Side (Top) | Middle | Right Side (Bottom)"
  ) -> a2
```

```{r,fig.width=10, fig.height=12}

grid.arrange(a1, a2, nrow = 2)

```

Column {data-width=400}
---

### Goal Differential Through the Season (Including Forfeited Games)

```{r differential over timeline, fig.height=5 }

schedule %>% 
  mutate(
    goals_for = cumsum(our_goals), 
    goals_against = cumsum(our_conceded), 
    
    differential = goals_for - goals_against
  ) %>% 
  select(game, Date, goals_for, goals_against, differential, opponent) %>% 
  
  pivot_longer(
    cols = c("goals_for", "goals_against"), 
    values_to = "Val", 
    names_to = "Type"
  ) %>% 
  
  mutate(
    Type = case_when(
      Type == "goals_for" ~ "Goals Scored", 
      T ~ "Goals Conceded"
    )
  ) -> plot_df

max(
  max(cumsum(schedule$our_goals)) + 1, 
  max(cumsum(schedule$our_conceded)) + 1
) -> plot_y_limit


plot_df %>% 
  plot_ly(
    x = ~game,
    y = ~Val,
    color = ~Type,
    colors = c("red", "#36c959"),
    
    type = "scatter",
    mode = "lines+markers", 
    
    text = 
      with(. , 
           paste(
             "Date: ", Date, 
             "<br>Opponent: ", opponent, 
             "<br>Goals:", Val, 
             "<br>Type: ", Type, 
             "<br>Differential", differential
    )), 
    
    hoverinfo = "text"
  ) %>% 
  layout(
    yaxis = list(
      range = c(0, plot_y_limit), 
      title = "Goals For and Against"
    ), 
    xaxis = list(
      title =   "Game #"
    ),
    legend = list(
      orientation = "h", y = -.5
      )
    )


```

### Goal Differential Distribution By Game (Excluding Forfeited Games)

```{r , fig.width=8, fig.height=6.5}

schedule %>% 
  mutate(
    differential = our_goals - our_conceded
  ) -> schedule

schedule %>% 
  ggplot(aes(x = differential)) + 
  geom_histogram(
    binwidth = 1, 
    color = "black", 
    fill = "blue"
    ) + 
  
  scale_x_continuous(
    labels = seq(from = min(schedule$differential), 
                 to =  max(schedule$differential), 
                 by = 1),
    
    breaks = seq(from = min(schedule$differential), 
                 to =  max(schedule$differential), 
                 by = 1)
  ) + 
  
  scale_y_continuous(
    breaks = function(x) int_breaks(x, n = 10)
  ) + 
  
  theme_minimal() + 
  
  xlab("Goal Differential") + 
  ylab("Count") + 
  
  ggtitle(
    paste0("Average per Game: ",
           case_when(mean(schedule$differential) > 0 ~ '+ ',
                     T ~ ''),
          round(mean(schedule$differential), 4))
  ) + 
  
  theme(text = element_text(size = 20))

```

Row {data-width=250 .tabset}
-------------------------------------

### Goals Details 

```{r}
custom_page_1_font = 14
col_title_font = 11
```

```{r }

scores %>% 
  filter(Action == "Goal") %>% 
  group_by(`Shot Type`) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  rename(
    Type = `Shot Type`
  ) %>% 
  mutate(id = seq(from = 1, to = nrow(.), by = 1)) -> shot_types

n_shot_types <- nrow(shot_types)

scores %>% 
  filter(Action == "Goal") %>% 
  group_by(`Position`) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  rename(
    Type = `Position`
  ) %>% 
  mutate(id = seq(from = 1, to = nrow(.), by = 1)) -> shot_loc

n_shot_loc <- nrow(shot_loc)

shot_sum <- merge(shot_types %>% na.omit(), shot_loc %>% na.omit(), by = "id", all = T) %>% select(-id)

shot_sum <- 
  shot_sum %>% 
  mutate_all(as.character)

shot_sum <- 
  shot_sum %>%  
    mutate_all(~replace(., is.na(.), ""))

shot_sum %>% 
  kable(align = c('l', 'c', 'l', 'c'), 
        col.names = c("Shot Type", "Number of Goals", "Shot Location", "Number of Goals")) %>% 
  kable_styling(bootstrap_options = c("condesed", "striped"),
                font_size = custom_page_1_font) %>% 
  column_spec(
    2, 
    border_right = T
    ) %>% 
  row_spec(0, font_size = col_title_font)

```

### Assists Details 

```{r}

scores %>% 
  filter(Action == "Assist") %>% 
  group_by(`Pass Type`) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  rename(
    Type = `Pass Type`
  ) %>% 
  mutate(id = seq(from = 1, to = nrow(.), by = 1))-> pass_types

n_shot_types <- nrow(pass_types)

scores %>% 
  filter(Action == "Assist") %>% 
  group_by(`Position`) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  rename(
    Type = `Position`
  ) %>% 
  mutate(id = seq(from = 1, to = nrow(.), by = 1)) -> pass_loc

n_shot_loc <- nrow(pass_loc)

shot_sum <- merge(pass_types %>% na.omit(), pass_loc %>% na.omit(), by = "id", all = T) %>% select(-id)

shot_sum <- 
  shot_sum %>% 
  mutate_all(as.character)

shot_sum <- 
  shot_sum %>% 
    mutate_all(~replace(., is.na(.), ""))

shot_sum %>% 
  kable(align = c('l', 'c', 'l', 'c'),  
        col.names = c("Assist Type", "Number of Ast.", "Assist Location", "Number of Ast.")) %>% 
  kable_styling(bootstrap_options = c("condesed", "striped"),
                font_size = custom_page_1_font)  %>% 
  column_spec(
    2, 
    border_right = T
    ) %>% 
  row_spec(0, font_size = col_title_font)

```

Individual Performance 
===

Column
---

### Personal Goal Ccontributions

```{r}

scores %>% 
  filter(Action == "Assist") %>% 
  group_by(Player) %>% 
  summarise(Assists = n()) %>% 
  arrange(-Assists) -> ast

scores %>% 
  filter(Action == "Goal") %>% 
  group_by(Player) %>% 
  summarise(Goals = n()) %>% 
  arrange(-Goals) -> gls

merge(gls, ast, all = T, by = "Player") -> all_

all_$Assists <- ifelse(is.na(all_$Assists), 0, all_$Assists)
all_$Goals <- ifelse(is.na(all_$Goals), 0, all_$Goals)
all_$`Goals + Assists` <- all_$Assists + all_$Goals

all_$`% Team's Goals` = paste0(round(all_$Goals/Goals_total,2)*100, "%")

all_ <- 
  inner_join(
    x = all_, 
    y = games_played %>% rename(`Games Played` = games_played), 
    by = "Player"
  )

all_ <- 
  all_ %>% arrange(-`Goals + Assists`, -Goals, -Assists, Player) %>% 
  select(Player, `Games Played`, `Goals`, `% Team's Goals`, Assists, `Goals + Assists`)

all_ %>% 
  kable(align = 'c') %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"))
```

Column 
---

### Assists Details

#### Assist Destinations 

```{r }

linkups <- 
  scores %>% filter(Action == "Goal") %>% 
    select(Date, Opponent, Score, Player, `Player Position`, `Play Type`) %>% 
    rename(Scorer = Player) %>% 
  
  left_join(
    scores %>% filter(Action == "Assist") %>% 
      select(Date, Opponent, Score, Player) %>% 
      rename(Assister = Player), 
    
    by = c("Date", "Opponent", "Score")
  )

linkups %>% 
  group_by(Assister) %>% 
  summarise(total_assist = n()) %>% 
  filter(!is.na(Assister)) %>% 
  
  left_join(
    linkups %>% 
      group_by(
        Assister, Scorer
      ) %>% 
      summarise(
        person_assists = n()
      ), 
    
    by = "Assister"
  ) %>% 
  
  arrange(-total_assist , Assister) -> advanced_assist_tally

advanced_assist_tally <- 
  advanced_assist_tally %>% 
  
  mutate(
    p_total = paste0(round(person_assists / total_assist, 2) * 100, "%")
  ) %>% 
  
  arrange(-total_assist, -person_assists)

advanced_assist_tally %>% 
  kable(align = 'c', 
        col.names = c(
          "Assist Creator", "Total Assists Given", 
          "Assist Recipient", "Assists to Recipient", "% of Assist Creator Total"
        )) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"))
```

#### Assist-less Goals

```{R}

assistless <- 
  
  linkups %>% filter(is.na(Assister) ) %>% 
  group_by(
    Scorer
  ) %>% 
  summarize(Goal = n()) %>% 
  rename(Player = Scorer) %>% 
  arrange(-Goal) %>% 
  merge(gls, by = "Player") %>% 
  
  mutate(
    p_total = paste0(round(Goal / Goals_total, 2) * 100, "%")
  ) %>% 
  
  select(-Goals)

assistless %>% 
  kable(align = 'c', 
        col.names = c(
          "Player", "Assist-less Goals", "% Of Team's Total"
        )) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"))

```

Column 
---

### Dynamic Duos

* Players in a Duo assist each other for goals

* A total is sourced from a table in `Assist Destinations` table 

```{r}

# variable `Goals_total` was taken from the beginning of the file. Created for th first Value Box 

advanced_assist_tally %>% 
  
  rowwise() %>%
  mutate(new_column = paste(sort(unique(c(Assister, Scorer))), collapse = " and ")) %>% 
  group_by(new_column) %>% 
  summarise(total = sum(person_assists)) %>% 
  arrange(-total)  %>% 
  mutate(p_total  = paste0(round(total/Goals_total,2) * 100 , "%")) %>% 
  
  kable(align = 'c', 
        col.names = c(
          "Players in Duo", "Total Goals Scored ", "% of Team's Goals"
        )) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"))

```

Map of Goals 
===

<!-- column with shiny-esque filters --> 
Column {data-width=300}
---

### Filters 

```{r}

scores %>% filter(Action == "Goal") %>%
  mutate(end_X = 100, 
         end_Y = 50, 
         handle = paste0(
           Player, " ", Score, " vs. ", Opponent, " on ", Date
         )) %>% 
  select(-`Pass Type`)-> goals_to_viz 

goals_to_viz <- 
  left_join(goals_to_viz, 
            scores %>% filter(Action == "Assist") %>% 
              select(Date, Opponent, Score, Player, `Pass Type`, `Loc Y`, `Loc X`, Hudson) %>% 
              rename(Assit_prov = Player, 
                     Assist_X = `Loc X`, 
                     Assist_Y = `Loc Y`, 
                     Assist_Hudson = Hudson
                     ), 
            by = c("Date", "Opponent", "Score")
            )

goals_to_viz <- 

  goals_to_viz %>% 
    group_by(handle ) %>% 
    mutate(id = 1:n(), 
           c = n()) %>% 
    ungroup() %>%
    
    mutate(handle = case_when(c == 2 ~ paste0("Part ", id, ": ", handle), 
                              T ~ handle)
           ) %>% 
    select(-id, -c)


selectInput(inputId = 'select_goal', 
              label = "Select a Goal", 
              choices = goals_to_viz$handle, 
              selected = goals_to_viz$handle[1])

```

Column {data-width=750}
--- 

### Maps

```{r fucntion show_one_goal}

boom_image = "boom2-small.jpg"

show_one_goal <- 
  function(which_goal){
    
    goals_to_viz %>% filter(handle == which_goal) -> plot_df
    
    scorer_label_x_mod <- ifelse(plot_df$Assist_X > plot_df$`Loc X`, -2, 2)
    scorer_label_x_mod <- ifelse(is.na(scorer_label_x_mod), 0, scorer_label_x_mod)
    
    scorer_label_y_mod <- ifelse(plot_df$Assist_X > plot_df$`Loc X`, 5, -5)
    scorer_label_y_mod <- ifelse(is.na(scorer_label_y_mod), 0, scorer_label_y_mod)
    
    scorer_label_x_mod <- ifelse(plot_df$`Loc X` > 95, scorer_label_x_mod - 5, scorer_label_x_mod)
    
    ###############
    
    assist_label_y_mod <- ifelse(plot_df$Assist_X > 95, -5, 0)
    assist_label_y_mod <- ifelse(is.na(assist_label_y_mod), 0, assist_label_y_mod)
    
    assist_label_x_mod <- ifelse(plot_df$Assist_X > 95, -5, 0)
    assist_label_x_mod <- ifelse(is.na(assist_label_x_mod), 0, assist_label_x_mod)
    
    # <--> 
    assist_label_y_mod <- ifelse(plot_df$Assist_X < 5, 5, 0)
    assist_label_y_mod <- ifelse(is.na(assist_label_y_mod), 0, assist_label_y_mod)
    
    assist_label_x_mod <- ifelse(plot_df$Assist_X < 5, 5, 0)
    assist_label_x_mod <- ifelse(is.na(assist_label_x_mod), 0, assist_label_x_mod)
    
    ###############
    
    boom_jpeg = NULL
    if(plot_df$Position == "Outside the Box"){
      boom_jpeg = geom_image(aes(x = 98, y = 50), image = boom_image, size = 0.15)
    }
    
    small_add_to_goal_loc <- 0
    if(plot_df$Position == "Outside the Box"){
      small_add_to_goal_loc = 2
    }
    
    position_coords =
      expand.grid(
        x = seq(from = 0, to = 100, by = 100), 
    #    coord2 = c(50,50,35,40,65,50,55,85,80,90,60,15, 20, 15,90)
        y = seq(from = 0, to = 100, by = 100)
      ) 
    
     ggplot(data = position_coords,
       aes(x = x, y = y)) +
       theme_void() + 
       geom_rect(aes(xmin = 0, xmax = 100, 
                      ymin = 0, ymax = 100), 
                  fill = PITCH_FILL) + 
       
       boom_jpeg + 
       annotate_pitch(colour = "white", fill = NULL) + 
       coord_flip(xlim = c(52, 100), ylim = c(0, 100)) + 
      
     
       # this is an assist 
       geom_segment(aes(x = plot_df$Assist_X , 
                        y = plot_df$Assist_Y , 
                        
                        xend = plot_df$`Loc X`,
                        yend = plot_df$`Loc Y`),
                    color = "grey", linetype = "dashed", linewidth = 1, 
                    arrow = arrow(length = unit(.5, "cm"))
                    ) + 
       # this is a shot 
       geom_segment(aes(x = plot_df$`Loc X`, 
                        y = plot_df$`Loc Y`, 
                        
                        xend = plot_df$end_X - small_add_to_goal_loc,
                        yend = plot_df$end_Y),
                    color = "blue", linewidth = 1, 
                    arrow = arrow(length = unit(.5, "cm"))
                    ) + 
       
       geom_label(aes(x = plot_df$Assist_X + assist_label_x_mod, 
                      y = plot_df$Assist_Y + assist_label_y_mod), 
                      fill = "grey", 
                      label = plot_df$Assit_prov,
                      size = 10) + 
       
       geom_label(aes(x = plot_df$`Loc X` + scorer_label_x_mod, 
                      y = plot_df$`Loc Y` + scorer_label_y_mod), 
                      fill = "blue", 
                      color = "white", 
                      label = plot_df$Player, 
                      size = 10)
    
  }

```

* Please don't mind inverted arc on top of the box. Fixing it will take too much effort...

```{r}
output$map_goal = renderPlot(show_one_goal(input$select_goal))

plotOutput('map_goal')
```


Column {data-width=400}
---

### Description

#### *All descriptions were meant to sound like Ray Hudson*

```{r}
HTML("<br>")
```

```{r}

output$text_assist <- renderText({
  m = goals_to_viz %>% filter(handle == input$select_goal) %>% select(Assist_Hudson) %>% unlist()
  
  ifelse(is.na(m), "", m)
})

output$text_goal <- renderText({
  goals_to_viz %>% filter(handle == input$select_goal) %>% select(Hudson) %>% unlist()
})

textOutput('text_assist')

```

```{r}
HTML("<br>")
```

```{r}
textOutput('text_goal')
```



Raw Data 
=== 

```{r}

datatable(
  scores %>% 
    mutate(Date = as.Date(Date)) %>% 
    select(-`Game Half`, -`Season Half`, - `Group`, -`Loc X`, -`Loc Y`, -Message)
  ,
  options = list("pageLength" = 25), 
  rownames = FALSE
  )

```